### 2019-08-23 README.Rmd
Added text to step 4 in README and vignette

>>>>

This function generates a grouped bar plot using ggplot2 and the
ggnewscale package. KEGG pathways are plotted on the y-axis and fold
enrichment is plotted on the x-axis. each KEGG pathway has a bar plotting
its fold enrichment in list 1 (red) and its fold enrichment in list 2 (blue).
The transparency of the bars correspond to the adjusted p-value for the
pathway's enrichment in the given list. The p-value presented as text to the
right of each pair of bars is the adjusted p-value associated with the
differential enrichment of the pathway between the two lists, and the pathways
are ordered from top to bottom by this p-value (i.e. smallest p-value on top
of plot, and largest p-value on bottom of plot).
